---
title: "Decayed Returns Volatility Curves"
author: "Jack K. Rasmus-Vorrath"
date: "July 22, 2017"
output: 
  html_document:
    keep_md: true
---

#The following calculates log returns and volatility measures of time series data on Intel Corporation stock performance using three different decay factors.

```{r Import}
library(tseries)
options("getSymbols.warning4.0"=FALSE)
options("getSymbols.yahoo.warning"=FALSE)
INTCdata <- get.hist.quote('INTC', quote = 'Close')
head(INTCdata)
```

##Lagged Log Returns
```{r Log Returns}
INTCret <- log(lag(INTCdata)) - log(INTCdata)
head(INTCret)
```

##Calculated Volatility Measure
```{r Volatility}
INTCvol <- sd(INTCret) * sqrt(250) * 100
INTCvol
```

##Exponentially Downweighted Continuous Lookback Window
```{r Downweighted Volatility}
Vol <- function(d, logrets){
  var = 0
  lam = 0
  varlist <- c()
  for (r in logrets){
    lam = lam*(1 - 1/d) + 1
    var = (1 - 1/lam)*var + (1/lam)*r^2
    varlist <- c(varlist, var)
  }
  sqrt(varlist)
}
volest <- Vol(10, INTCret)
head(volest)
volest2 <- Vol(30, INTCret)
head(volest2)
volest3 <- Vol(100, INTCret)
head(volest3)
```

##Plotted Volatility Curves
```{r Volatility Curves}
plot(volest, type = 'l')
lines(volest2, type = 'l', col = 'red')
lines(volest3, type = 'l', col = 'blue')
```

#The volatility curve with decay factor 0.99 demonstrates substantially smoother features.
